Priors

### 2023-06-25 reports/priors.Rmd
update figures

@@

ctis %>%
  ggplot(aes(x = beta, fill=state)) +
  geom_density() +
  scale_fill_viridis(option="mako", discrete=TRUE) +
  theme_c()

ctis %>%
  ggplot(aes(x = beta, fill=state)) +
  geom_density() +
  scale_fill_viridis(option="mako", discrete=TRUE) +
  theme_c() +
  facet_wrap(~state)

@@

>>>>

```{r, fig.height=7}

ctis %>%
  group_by(state) %>%
  summarize(median = median(beta, na.rm=TRUE),
            mean = mean(beta, na.rm=TRUE),
            q1 = quantile(beta, .025,  na.rm=TRUE),
            q2 = quantile(beta, .975,  na.rm=TRUE)) %>%
  ggplot(aes(y=fct_reorder(state, mean, .desc=TRUE))) +
  ggridges::geom_density_ridges(
    aes(x=beta,
        y=fct_reorder(state, beta, .fun =mean)),
    data=ctis,
    fill="#596281",
    quantile_lines=TRUE,
    quantiles = c(.025,.975),
    quantile_fun=function(beta,...) c(
                                    #  quantile(beta,.025, na.rm=TRUE),
                                      mean(beta,na.rm=TRUE)
                                    #  quantile(beta,.975, na.rm=TRUE)
                                      )) +
  # geom_errorbar(aes( xmin=q1,xmax=q2),width=.2) +
  scale_x_continuous(n.breaks=10, limits=c(0,1)) +
  labs(x= TeX("Empirical Estimates of $\\beta$"),
       y="State",
       title = TeX("Empirical Estimates of $\\beta$ from the COVID-19 Trends and Impact Survey"),
       subtitle = "Density Estimate of Distribution and Mean by State" ) +
  theme_c(axis.title=element_text(size=12),
          axis.text.x=element_text(size=11))

@@

ctis %>%
  ggplot(aes(x = beta, fill=state)) +
  geom_density(alpha=.6) +
  scale_fill_viridis(option="mako", discrete=TRUE) +
  theme_c()

@@

```{r,include=FALSE}
ctis %>%
  ggplot(aes(x = beta, fill=state)) +
  geom_density() +
  scale_fill_viridis(option="mako", discrete=TRUE) +
  theme_c() +
  facet_wrap(~state)
